Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-12-12 paper/paper.Rmd
making lots of changes

@@

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Image descriptions that are associated with the attributes of each image.")
```

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Possible face descriptions for each individual face. Most of the selections were obvious for each image, with the exception of obscured and head angle.")
```

@@

### Face detection rate modelled in characteristics

A logistic regression model was used to assess the characteristics of the face and scene affecting detection.

A step wise method was used to determine the best regression model.

@@

knitr::kable(ModelEstimatesTable, format = "latex", align=c("l", 
                                          "r", "l",
                                          "r", "l",
                                          "r", "l",
                                          "r", "l"),
             booktabs = TRUE, longtable=FALSE, caption="Evaluation of factors affecting face recognition by API. (** 0.01 * 0.05 . 0.01 - NS) Coefficients from logitics regression models shown. Glasses, visorhat, headangle lighting, shotangle and situation all contribute significantly to face detection.")
```

For the most part, the APIs were all affected by the same factors.
The factors that negatively affected all APIs were glasses, visor or hat. Background only negatively affected Google. Situation had different effects on each API.
Results for Google were most interestng in the shotangle had differing effects on the detection.

>>>>

*** (1) Check caption sentences finish with "." (2) Check spelling (3) Check no referring to tables and figures in the text like "the table below ..." or the "figure above ..." (4) Check all the writing is in third person, remove "We then ..." (5) One sentence paragraphs should be very rarely used, and I suspect there are too many in the current draft. Check if the orphan sentence better belongs with the prior or after paragraph.

@@

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics recorded for each image.")
```

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics recorded for each  face. Most were easy to assess for each face, with the exception of obscured and head angle.")
```

@@

### Modeling detection rate

A logistic regression model was used to assess the characteristics of the face and scene affecting detection, with stepwise variable selection. The binary response was whether the face was detected or not, using the manually tagged data as the benchmark, and characteristics included the setting, angle of shot and player, background, lighting and player adornments. (*** Any other variables considered but not selected for any model?)
A separate model was fit for each API.

@@

knitr::kable(ModelEstimatesTable, format = "latex", align=c("l", 
                                          "r", "l",
                                          "r", "l",
                                          "r", "l",
                                          "r", "l"),
             booktabs = TRUE, longtable=FALSE, caption="Evaluation of factors affecting face recognition for API, as assessed by logistic regression model. Coefficients from the four models shown (significance: ** 0.01 * 0.05 . 0.01 - NS). Most APIs wre affected by similar factors, with glasses, visor or hat, head angle, lighting, shot angle and situation all contributing significantly to face detection.")
```

*** The number of digits should be consistent, e.g. "-1" should be "-1.00". I don't know how to force this with the kable printing, but one way or another we have to.

For the most part, the APIs were all affected by the same factors. Those that negatively affected all APIs were glasses, visor or hat. Background only negatively affected Google's detection rate. Situation had different effects on each API.
Results for Google were most interestng in the shotangle had differing effects on the detection.
